Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-31 journal/article.tex
T: Public events

>>>>

% Seminars and public events

% What public events
Organizations typically strived to increase the agile awareness by introducing
series of events for promoting agile, ranging from public seminars to brown bag
meetings and hands-on workshops. These events were aimed at a general audience,
consisting of all organizational groups. Events were arranged especially in the
beginning of the agile journey. In some cases the demand and interest in public
events was maintained, and the events were continued.
Some cases describe continually arranged agile events serving a central role in
maintaining and advancing further the agile model [P23, P47].
Training events were even productized so that they could be replicated for a
large number of people [P32, P46].

% Content of events
In addition to general training and enabling awareness, the purpose of agile
events was to evangelize and expand the agile model throughout the organization
[P1, P10, P23, P32, P46].
Workshops were used to get people better involved [P16], and public lectures
were used to set straight sidetracks in the agile implementation[P26].
Hands-on workshops were used as a more engaging teaching method compared to
traditional lectures [P32, P41]. Open events were good for delivering the same
message to many people at the same time. As everyone could heard the same
questions and answers the understanding was consistent [P9, P41].
Workshops were arranged for identifying problems and planning the new model [P7,
P16, P27].
